### 2011-11-14 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

\noindent
I would like to thank everyone participating in the jInfer project for creating a~solid foundation for this work, namely Irena Mlýn\-ko\-vá, Mi\-chal Klem\-pa, Má\-rio Mi\-ku\-la, Ro\-bert Sme\-ta\-na and Mi\-chal Švi\-rec. The thanks goes again to Ms. Mlýn\-ko\-vá for supervising this work, as well as everyone reviewing it, in no~particular order Lý\-dia Šva\-ger\-ko\-vá, Mi\-chal Šva\-ger\-ka, Zu\-za\-na Ma\-sá\-ro\-vá, Mi\-chal Ke\-se\-ly and others.

@@

\hbox{\hbox to 0.5\hsize{%
In ........ date ............
\hss}\hbox to 0.5\hsize{%
signature
\hss}}

>>>>

\noindent
I would like to thank everyone participating in the jInfer project for creating a~solid foundation for this work, namely Irena Mlýn\-ko\-vá, Mi\-chal Klem\-pa, Má\-rio Mi\-ku\-la, Ro\-bert Sme\-ta\-na and Mi\-chal Švi\-rec. The thanks goes again to Ms. Mlýn\-ko\-vá for supervising this work, as well as everyone reviewing it, in no~particular order Lý\-dia Šva\-ger\-ko\-vá, Mi\-chal Šva\-ger\-ka, Zu\-za\-na Ma\-sá\-ro\-vá, Mi\-chal Ke\-se\-ly and others\textsuperscript{HB}.

@@

\hbox{\hbox to 0.5\hsize{%
In ........ date ............
\hss}\hbox to 0.5\hsize{%

\hss}}
